Parametrization of Invertible Resnets up to Homology Equivalence for Abelian Lie Groups

### 2020-04-02 llncs2e/paper77.tex
notation

\subsection{Decomposition of Connected Commutative Lie groups}
\label{decomposition}
\begin{theorem}{\cite[p.~116,~p.~26]{onishchik1993lie,van2003lie}}
\label{connectedcommutativeliegroupdecomposition}
Every connected commutative (or in other words abelian) Lie group $G$ is isomorphic to some product space $\mathbb{T}^p \times \mathbb{R}^q$ with $\dim G = p+q$, i.e. $G \simeq \mathbb{T}^p \times \mathbb{R}^q$.
\end{theorem}

@@

Since $\mathfrak{g}$ is a linear space, we can extend the basis $\mathbb{Z}\omega_1 \oplus \cdots \oplus \mathbb{Z} \omega_n$ to the whole Lie algebra $\mathfrak{g}$. Thus we get a linear isomorphism $\varphi: \mathfrak{g} \rightarrow \mathbb{R}^n$, where $\mathbb{R}^n \simeq \mathbb{R}^p \times \mathbb{R}^q$ with $p+q = n$. The map $\text{exp} \circ \varphi^{-1}: \mathbb{R}^n \rightarrow G$ is a surjective Lie group homomorphism, i.e. a group homomorphism that is smooth, with smooth inverse. According to the Isomorphism Theorem for groups, this group also factorizes by a bijective group homomorphism \cite[pp.~5-7]{van2003lie}:
\[
\begin{tikzcd}[column sep=huge]
    \displaystyle \mathfrak{g}
    \arrow[swap]{r}{\varphi}
    \arrow[bend left=25]{rr}{\text{exp}}
    \arrow[swap]{dr}{\pi \; \circ \; \varphi}
&   \mathbb{R}^p \times \mathbb{R}^q
    \arrow{d}{\pi}
    \arrow[swap]{r}{\text{exp} \; \circ \; \varphi^{-1}}
&   G\\	
&   (\mathbb{R}/\mathbb{Z})^p \times \mathbb{R}^q 
	\arrow[swap]{ur}{\overline{\text{exp} \; \circ \; \varphi^{-1}}}
\end{tikzcd}
\]
The canonical map $\pi: \mathbb{R}^n \simeq \mathbb{R}^p \times \mathbb{R}^q \rightarrow (\mathbb{R}/\mathbb{Z})^p \times \mathbb{R}^q$ is locally diffeomorphic and $\overline{\text{exp} \circ \varphi^{-1}} \circ \pi$ as well. Due to the homogeneity of commutative lie groups, the map is everywhere a diffeomorphism. The projection $\overline{\text{exp} \; \circ \; \varphi^{-1}}$ is bijective, thus also a diffeomorphism and thus an isomorphism of Lie groups. By definition $\mathbb{R}^n/\mathbb{Z}^n \simeq (\mathbb{R}/\mathbb{Z})^n \simeq \mathbb{T}^n$ and the proof follows. \qed
\end{proof}

@@

\subsubsection{Non-invertible $\xi_i$- and $\psi_i$-Architecture}
The invertible architecture, which is described in Sect. \ref{subsec:invertibleneuralnets}, uses the partially linear functions $\xi_1,\xi_2$ and $\psi_1,\psi_2$, which are parameterized during the learning process. The architecture is taken from the work of Ardizzone et al. \cite{ArdizzoneKRK19}. These functions are to be learned and are composed in a trivially invertible way, see Sect. \ref{subsec:invertibleneuralnets}. The functions themselves are implemented as neural subnets. Each function is a $\mathcal{C}^1$-net as described in Sect. \ref{resnet}, with a total of $3$ dense layers. The vector $\mathbf{u}_{1}^{(l)} \in \text{M}(n,\mathbb{R})$ is transformed by $\xi_1,\xi_2,\psi_1,\psi_2: \text{M}(n,\mathbb{R}) \rightarrow \text{M}(n,\mathbb{R})$, such that the dimension of the vector does not change. The leaky rectifying linear unit activation function has been selected for every layer in the subnet:
\begin{align}
	\text{LeakyReLu}(\mathbf{x}^{(l)}) = 
	\begin{dcases}
	    \mathbf{x}^{(l)}_{i},
	    & \text{if} \; \mathbf{x}^{(l)}_{i} \geq 0, \\
	    5.5 \cdot \mathbf{x}^{(l)}_{i}
	    & \text{if} \; \mathbf{x}^{(l)}_{i} < 0.
	\end{dcases}
\end{align}
We apply batch normalization after the activation function, see Appx. \ref{appx:invarch}. The partition of the vector is still an open research question \cite{ArdizzoneKRK19}. We divide the flattened vector precisly into two halfs, since the samples are square matrices:
\begin{align}
\mathbf{x}^{(l)} = (\mathbf{u}^{(l)}_1, 0, \cdots, 0) + (0, \cdots, 0, \mathbf{u}^{(l)}_2).
\end{align}

>>>>

\subsection{Decomposition of Connected Commutative Lie groups}
\label{decomposition}
\begin{theorem}{\cite[p.~116,~p.~26]{onishchik1993lie,van2003lie}}
\label{connectedcommutativeliegroupdecomposition}
Every connected commutative (or in other words abelian) Lie group $G$ is isomorphic to some product space $\mathbb{R}^p \times \mathbb{T}^q$ with $\dim G = p+q$, i.e. $G \simeq \mathbb{R}^p \times \mathbb{T}^q$.
\end{theorem}

@@

Since $\mathfrak{g}$ is a linear space, we can extend the basis $\mathbb{Z}\omega_1 \oplus \cdots \oplus \mathbb{Z} \omega_n$ to the whole Lie algebra $\mathfrak{g}$. Thus we get a linear isomorphism $\varphi: \mathfrak{g} \rightarrow \mathbb{R}^n$, where $\mathbb{R}^n \simeq \mathbb{R}^p \times \mathbb{R}^q$ with $p+q = n$. The map $\text{exp} \circ \varphi^{-1}: \mathbb{R}^n \rightarrow G$ is a surjective Lie group homomorphism, i.e. a group homomorphism that is smooth, with smooth inverse. According to the Isomorphism Theorem for groups, this group also factorizes by a bijective group homomorphism \cite[pp.~5-7]{van2003lie}:
\[
\begin{tikzcd}[column sep=huge]
    \displaystyle \mathfrak{g}
    \arrow[swap]{r}{\varphi}
    \arrow[bend left=25]{rr}{\text{exp}}
    \arrow[swap]{dr}{\pi \; \circ \; \varphi}
&   \mathbb{R}^p \times \mathbb{R}^q
    \arrow{d}{\pi}
    \arrow[swap]{r}{\text{exp} \; \circ \; \varphi^{-1}}
&   G\\	
&   (\mathbb{R})^p \times \mathbb{R/\mathbb{Z}}^q 
	\arrow[swap]{ur}{\overline{\text{exp} \; \circ \; \varphi^{-1}}}
\end{tikzcd}
\]
The canonical map $\pi: \mathbb{R}^n \simeq \mathbb{R}^p \times \mathbb{R}^q \rightarrow \mathbb{R}^p \times (\mathbb{R}/\mathbb{Z})^q$ is locally diffeomorphic and $\overline{\text{exp} \circ \varphi^{-1}} \circ \pi$ as well. Due to the homogeneity of commutative lie groups, the map is everywhere a diffeomorphism. The projection $\overline{\text{exp} \; \circ \; \varphi^{-1}}$ is bijective, thus also a diffeomorphism and thus an isomorphism of Lie groups. By definition $\mathbb{R}^q/\mathbb{Z}^q \simeq (\mathbb{R}/\mathbb{Z})^q \simeq \mathbb{T}^q$ and the proof follows. \qed
\end{proof}

@@

\subsubsection{Non-invertible $\xi_i$- and $\psi_i$-Architecture}
The invertible architecture, which is described in Sect. \ref{subsec:invertibleneuralnets}, uses the partially linear functions $\xi_1,\xi_2$ and $\psi_1,\psi_2$, which are parameterized during the learning process. The architecture is taken from the work of Ardizzone et al. \cite{ArdizzoneKRK19}. These functions are to be learned and are composed in a trivially invertible way, see Sect. \ref{subsec:invertibleneuralnets}. The functions themselves are implemented as neural subnets. Each function is a $\mathcal{C}^1$-net with a total of $3$ dense layers, see Sect. \ref{resnet}. The vector $\mathbf{u}_{1}^{(l)} \in \text{M}(n,\mathbb{R})$ is transformed by $\xi_1,\xi_2,\psi_1,\psi_2: \text{M}(n,\mathbb{R}) \rightarrow \text{M}(n,\mathbb{R})$, such that the dimension of the vector does not change. The leaky rectifying linear unit activation function has been selected for every layer in the subnet:
\begin{align}
	\text{LeakyReLu}(\mathbf{x}^{(l)}) = 
	\begin{dcases}
	    \mathbf{x}^{(l)}_{i},
	    & \text{if} \; \mathbf{x}^{(l)}_{i} \geq 0, \\
	    5.5 \cdot \mathbf{x}^{(l)}_{i}
	    & \text{if} \; \mathbf{x}^{(l)}_{i} < 0.
	\end{dcases}
\end{align}
We apply batch normalization after the activation function, see Appx. \ref{appx:invarch}. The partition of the vector is still an open research question \cite{ArdizzoneKRK19}. We divide the flattened vector precisly into two halfs, since the samples are square matrices:
\begin{align}
\mathbf{x}^{(l)} = (\mathbf{u}^{(l)}_1, 0, \cdots, 0) + (0, \cdots, 0, \mathbf{u}^{(l)}_2).
\end{align}
